\documentclass[,article,oneside,notitlepage]{memoir}
\usepackage[T1]{fontenc}
%\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\usepackage{titlesec}
\usepackage{titling}


%Some pandoc variables
\def\myauthor{Andrew Garland}
\def\mytitle{Introduction}
\def\mysubtitle{SEP Mock Senate}
\def\mycopyright{\myauthor}
\def\myemail{}
\def\mydate{2013}
\def\myspacing{}
\def\mylandscape{}
%-----------------------------------
%Other customizations

%Restyle Page Titles

  \pretitle{\begin{flushleft}\huge}
  \posttitle{\large \vspace{-0.5em}\par\mysubtitle\vspace{3em}  \par\end{flushleft}\normalsize\vspace{0.25ex}}
  \preauthor{}
  \postauthor{}
  \predate{}
  \postdate{}
  
%Restyle Section Titles
\titleformat{\section}
	{\normalfont\Large}
	{\thesection}{1em}{\bfseries}
	
\titleformat{\subsection}
	{\normalfont\large}
	{\thesubsection}{1em}{\bfseries}
	
\titleformat{\subsubsection}
	{\normalfont}
	{\thesubsubsection}{1em}{\bfseries}
	
%\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
%\titlespacing\subsection{0pt}{9pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
%\titlespacing\subsubsection{0pt}{6pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
	
\titlespacing*{\section}{0pt}{*4}{*-0.75}
\titlespacing*{\subsection}{0pt}{*2.5}{*-0.5}
\titlespacing*{\subsubsection}{0pt}{*0.75}{*-1.5}

%Use custom linespacing if available


%Add color package
\usepackage{color}
\usepackage[usenames,dvipsnames,svgnames]{xcolor}

%Headers and footers
\textwidth=6in
\makepagestyle{senate}
\makeevenfoot{senate}{\small\color{gray}\mytitle}{\small\color{gray}\copyright\ \mydate\ by \myauthor}{\small\color{gray}p. \thepage}
\makeoddfoot{senate}{\small\color{gray}\mytitle}{\small\color{gray}\copyright\ \mydate\ by \myauthor}{\small\color{gray}p. \thepage}

\pagestyle{senate}

\renewcommand*{\sideparfont}{\scriptsize}
\sideparmargin{right}

\usepackage{multicol}

%-------------------------------------------------
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}

%Pick Palatino font for the mainfont if it's not specified already
			\setmainfont{Adobe Caslon Pro}
	  
\fi

%Set up landscape style
	\usepackage[top=1in, bottom=1in,top=1in,bottom=1in,footskip=0.5in]{geometry}


\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={Andrew Garland},
            pdftitle={Introduction},
            colorlinks=true,
            urlcolor=blue,
            linkcolor=red,
            pdfborder={0 0 0}}
\setlength{\parindent}{12pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}



\title{Introduction}
%\author{Andrew Garland}
%\date{2013}
\date{}

%\checkandfixthelayout %To set memoir margins, etc

\begin{document}
\maketitle
\thispagestyle{senate}

\section{Welcome!}

\section{What you should learn}

There are several general themes that we will focus on during these two
weeks. Here is a brief (incomplete) list of things that I hope you know
by the end of our time together:

\begin{multicols}{2}
\begin{enumerate}
\item{What the Senate does}
\item{Basic parliamentary procedure}
\item{Basic political theory}
\item{How to write a persuasive speech}
\item{How to write a policy plan}
\item{How to debate about public policy}
\item{Basic ideological positions of both U.S. political parties}
\end{enumerate}
\end{multicols}

\section{How this class will work}

You will be assigned a role to play. I will try to assign you to play a
senator of your choosing. Once your role is assigned, you will be
expected to play that role throughout the rest of our Senate activities.

We will try to model the actual working of the U.S. Senate. Because of
our time and size constraints, the model will have to be simplified
somewhat. But there should be enough similarity to give you a good sense
of how the Senate actually works.

I have a lot of information for you, and it will come very fast. But
once we get into Senate activities, most of our time will be taken up by
those activities and not my formal instruction.

\section{Expectations}

Here is a list of my primary expectations for you:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Participate
\item
  Be respectful (both of others' views and their desire to learn)
\item
  Play your role as well as you can
\item
  Write (or coauthor) at least one piece of legislation
\item
  Give at least two speeches on the floor
\end{enumerate}

\section{Schedule}

See the calendar handout.

\section{Talking to me}

I am very open to suggestions about doing things differently. If you
have an idea, please come talk to me about it.

Once we are in the writing and debating stage, I expect there will be
time for you to get personalized help from me about your writing and
speaking. I will provide what help I can, and you should feel free to
ask for it.

If something is not going well (whatever it is), please talk to me about
it as soon as you can.

\end{document}
